%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{purple}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.77]{geometry}

% personal data
\name{Todor}{Antić}
\title{25.12.2000.}     
\address{Prisoje 9}{6000 Koper}{Slovenia}
\phone[mobile]{+386~(070)~140~576}
\email{todorantic29@gmail.com}

\begin{document}

	\makecvtitle
	
	\section{Education}
		\cventry{2015--2019}{High School}{X gimnazija "Mihajlo Pupin"}{Belgrade - Serbia}{}{} 
		\cventry{2019--}{Bachelor}{University of Primorska}{Faculty of Mathematics, Natural Sciences and Information Technologies, \textit{Bachelor of Mathematics}}{Koper - Slovenia}{}

	\section{Experience}
		\cventry{2019-}{Science center Petnica}{Student associate}{}{}{In PSC I serve as a help to highschool students during their introduction to Computer Science and methods of scientific work and reasearch. Besides that I lector the papers for PSC publishment "Petnicke Sveske" for subjects Mathematics and Computer Science.}
		\cventry{2018-2018}{Scientific Institute Mihajlo Pupin}{Intern}{}{}{As intern in IMP I was a part of a project with Montenegrian Electrodistibution Network and French company ALSTOM. I made a GUI used to control the interactions between Trafo stations in Montenegro.}
		\cventry{2018-}{Freelancing}{}{}{}{As a freelancer I teach mathematics and physics to highschool students and do programming work, mostly as a web developer (HTML, CSS, JS) and Python.}

	\section{Languages}
		\cvitem{Serbian}{Native}
		\cvitem{English}{Fluent}
		\cvitem{French}{Basic}
		\cvitem{Slovene}{Basic}

	\section{Knowledge Area}
		\cvitem{Python}{Advanced}
		\cvitem{Javascript, HTML, CSS}{Advanced}
		\cvitem{C++}{Decent}
		\cvitem{Bash}{Beginner}
		
	\section{About me}
		\cvitem{Qualities}{I think of myself as a social person, capable of working as a part of a team or as an individual. I am a perfectionist and trive in a leading position.}
		\cvitem{Flaws}{I have a tendency to question authority and get into arguments and sometimes prolong them because of my own stuborness.}
		

\end{document}